\documentclass[11pt]{article}

% geometry definitions
\usepackage[margin=1in]{geometry}
\newcommand{\sectionwidth}{1in}		% define the width of left column
\newcommand{\globalitemsep}{0em}	% item sep for lists and bib
\newcommand{\globaltopsep}{0em}		% top sep for lists and bib
\newlength{\globalleftmargin}
\setlength{\globalleftmargin}{2em}	% left margin for lists and bib
\addtolength{\globalleftmargin}{\sectionwidth}	% add section width
\newcommand{\rulepadding}{0.5\baselineskip}	% added padding above and below title rules
\newlength{\upperpadding}
\setlength{\upperpadding}{-1ex}		% default upper padding for title rules (-1ex space makes gaps above and below title rule even without any additional padding)
\addtolength{\upperpadding}{\rulepadding}	% add additional padding
\newcommand{\subsectionskip}{\baselineskip}	% skip between subsections
\usepackage{changepage,etoolbox}			% to indent an entire paragraph
\AtBeginEnvironment{adjustwidth}{\partopsep0pt}	% remove vertical spacing

% custom formatting and style
\usepackage{titlesec}		% allow for section formatting
\titleformat{\section}[runin]{}{}{0em}{%
	\vspace*{\rulepadding}% adds padding below title rules
	\titlerule\newline%
	\vspace*{-\baselineskip}% aligns section and subsection
	\bfseries% font formatting
}
\titlespacing{\section}{0em}{\upperpadding}{*}	% -1ex space to make gap between titlerule even, plus additional \rulepadding
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}
\titlespacing{\subsection}{\sectionwidth}{0em}{*}
\titleformat{\subsubsection}[runin]{\itshape}{}{0em}{}[:]
\titlespacing{\subsubsection}{\sectionwidth}{0em}{*}

% hyperlinks
\usepackage{hyperref}		% custom hyperlinks
\hypersetup{%
	colorlinks=true,%
	allcolors=[RGB]{70,115,180}%
}							% hyperlink style settings

% custom title
\usepackage{titling}		% allow for custom titles
\renewcommand{\maketitle}{%
	\begin{center}
		{\huge\bfseries\theauthor}\\
		\vspace*{1em}% gap between author and contact
		{\href{mailto:\theemail}{\texttt{\theemail}}\qquad\href{https://\thewebsite}{\texttt{\thewebsite}}\qquad\href{\thescholar}{Google Scholar}}\\
		\vspace*{0em}% gap after contact
	\end{center}%
}							% title formatting

% custom lists
\usepackage{enumitem}		% allow for custom lists
\setlist{%
	itemsep=\globalitemsep,%
	topsep=\globaltopsep,%
	leftmargin=\globalleftmargin,%
	label=$\vcenter{\hbox{\tiny$\bullet$}}$%
}							% set default itemize/enumerate parameters

% custom page numbering
\usepackage{lastpage}		% determines last page number
\usepackage{fancyhdr}		% custom footers for page numbering
\pagestyle{fancy}			% use fancyhdr page numbering
\renewcommand{\headrulewidth}{0em}	% remove headrule from fancyhdr
\fancyhf{}					% clear default footer
\fancyfoot[C]{%
	\thepage\ of \pageref*{LastPage}%
}							% custom page numbering

% custom bibliography style
\bibliographystyle{cvstyle}	% use cvstyle.bst for bold author name
\makeatletter
\renewcommand\refname{Publications}	% change bibliography heading
\renewenvironment{thebibliography}[1]
{\section*{\refname}%
	* indicates co-first author and equal contribution.\\
	\vspace*{\subsectionskip}
	\@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
	\list{\@biblabel{\@arabic\c@enumiv}}%
	{\settowidth\labelwidth{\@biblabel{#1}}%
		\setlength\itemsep{\globalitemsep}
		\setlength\topsep{\globaltopsep}
		\leftmargin\globalleftmargin
		\@openbib@code
		\usecounter{enumiv}%
		\let\p@enumiv\@empty
		\renewcommand\theenumiv{\@arabic\c@enumiv}
	}%
	\sloppy
	\clubpenalty4000
	\@clubpenalty \clubpenalty
	\widowpenalty4000%
	\sfcode`\.\@m}
{\def\@noitemerr
	{\@latex@warning{Empty `thebibliography' environment}}%
	\endlist}
\makeatother

% other modifications and custom commands
\usepackage{bookmark}		% remove bookmark heirarchy warning
\setlength\parindent{0em}	% disable automatic indentation
\newcommand{\cvdate}[1]{\hfill#1}			% date style
\newcommand{\cvdates}[2]{\hfill#1\,--\,#2}	% dates style
\newcommand{\Cpp}{%
	C\nolinebreak[4]%
	\hspace*{-.05em}%
	\raisebox{.4ex}{\tiny\bf ++}%
}							% C++ symbol with centered + signs

% long/short cv versions
\usepackage{comment}
\includecomment{gpa-off}
\excludecomment{gpa-on}
\excludecomment{coursework}
\excludecomment{references}








\begin{document}
	
	% title
	\title{}
	\date{}
	\author{Brendon G.\ Anderson}
	\newcommand{\theemail}{bga@calpoly.edu}
	\newcommand{\thephone}{(760) 473-3007}
	\newcommand{\thewebsite}{brendon-anderson.github.io}
	\newcommand{\thescholar}{https://scholar.google.com/citations?user=kNA83jQAAAAJ&hl=en&oi=ao}
	\maketitle

	% research interests
	\section{\texorpdfstring{Research \\[\baselineskip] Interests}{Research Interests}}
	\hfill\vspace*{-2\baselineskip}

	\begin{adjustwidth}{\sectionwidth}{}I am interested in the development and analysis of \textbf{safe and reliable computational methods} by applying rigorous mathematics to interdisciplinary problems in the areas of \textbf{machine learning}, \textbf{optimization}, \textbf{control theory}, and \textbf{game theory}. My latest projects surround provable safety for neural networks using robust optimization theory, stability guarantees for evolutionary games using functional analysis, and robust control of distributed systems using optimal transport theory.\end{adjustwidth}

	% academic positions
	\section{\texorpdfstring{Academic \\[\baselineskip] Positions}{Academic Positions}}
	\hfill\vspace*{-2\baselineskip}
	\subsection{Assistant Professor}
	\cvdates{Sep.\ 2024}{Present}

	\hspace*{\sectionwidth}California Polytechnic State University

	\hspace*{\sectionwidth}Mechanical Engineering Department
	
	% education
	\section{Education}
	\subsection{University of California, Berkeley}
	\cvdates{Aug.\ 2018}{May 2024}
	
	\hspace*{\sectionwidth}Ph.D.\ in Mechanical Engineering (Major in Control Theory)

	\subsubsection{Dissertation}
	``\href{https://brendon-anderson.github.io/files/publications/dissertation.pdf}{Provably robust machine learning through structure-aware \\
	\hspace*{\sectionwidth}computation}''

	\subsubsection{Minors}
	Mathematics, Optimization
	
	\subsubsection{Advisor}
	\href{https://people.eecs.berkeley.edu/~sojoudi/}{Somayeh Sojoudi}
	
	\begin{gpa-on}
		\subsubsection{GPA}
		$3.906/4.0$
	\end{gpa-on}
	
	\vspace*{\subsectionskip}

	\subsection{University of California, Berkeley}
	\cvdates{Aug.\ 2022}{Dec.\ 2023}

	\hspace*{\sectionwidth}M.A.\ in Mathematics

	\subsubsection{Thesis}
	``\href{https://brendon-anderson.github.io/files/publications/ma_thesis.pdf}{Dissipativity theory for evolutionary games on infinite strategy sets}''

	\begin{gpa-on}
		\subsubsection{GPA}
		$3.925/4.0$
	\end{gpa-on}

	\vspace*{\subsectionskip}
	
	\subsection{University of California, Berkeley}
	\cvdates{Aug.\ 2018}{May 2020}
	
	\hspace*{\sectionwidth}M.S.\ in Mechanical Engineering (Major in Control Theory)
	
	\subsubsection{Thesis}
	``\href{https://brendon-anderson.github.io/files/publications/ms_thesis.pdf}{Towards optimality and robustness guarantees for data-driven learning \\
	\hspace*{\sectionwidth}and decision making}''
	
	\begin{gpa-on}
		\subsubsection{GPA}
		$4.0/4.0$
	\end{gpa-on}
	
	\vspace*{\subsectionskip}
	
	\subsection{University of California, Los Angeles}
	\cvdates{Sep.\ 2015}{Mar.\ 2018}
	
	\hspace*{\sectionwidth}B.S.\ in Mechanical Engineering
	\begin{gpa-off}
		(\textit{summa cum laude})
	\end{gpa-off}
	
	\subsubsection{Technical Breadth Area}
	Mathematics
	
	\begin{gpa-on}
		\subsubsection{GPA}
		$4.0/4.0$ (\textit{summa cum laude})
	\end{gpa-on}
	
	% research experience
	\section{\texorpdfstring{Research \\[\baselineskip] Experience}{Research Experience}}
	\hfill\vspace*{-2\baselineskip}

	\subsection{Graduate Student Researcher --- UC Berkeley}
	\cvdates{Aug.\ 2018}{May 2024}
	
	\subsubsection{Advisor}
	\href{https://people.eecs.berkeley.edu/~sojoudi/}{Somayeh Sojoudi}
	
	\vspace*{\subsectionskip}
	
	\subsection{Jr.\ Development Engineer --- UCLA Engineering}
	\cvdates{Jan.\ 2018}{Jun.\ 2018}
	
	\subsubsection{Advisor}
	\href{http://www.seas.ucla.edu/mcloskey/}{Robert M'Closkey}
	
	\vspace*{\subsectionskip}
	
	\subsection{Research Assistant --- UCLA Mathematics}
	\cvdates{Jun.\ 2017}{Aug.\ 2017}
	
	\subsubsection{Advisors}
	\href{https://brae.calpoly.edu/faculty-and-staff-haberland}{Matt Haberland}, \href{https://sites.google.com/msu.edu/turanova/home}{Olga Turanova}, and \href{http://www.math.ucla.edu/~bertozzi/}{Andrea L.\ Bertozzi}

	% awards and honors
	\section{\texorpdfstring{Awards and \\[\baselineskip] Honors}{Awards and Honors}}
	\hfill\vspace*{-2\baselineskip}
	\begin{enumerate}[label={\arabic*.}]
		\item First place in \href{https://www.informs.org/Publications/OR-MS-Tomorrow/OR-MS-Tomorrow-Mini-Poster-Competition-2023-Winners}{INFORMS OR/MS Mini-Poster Competition}
		\cvdate{Nov.\ 2023} \\
		\textit{For the paper ``\href{https://arxiv.org/pdf/2302.01961.pdf}{Asymmetric certified robustness via feature-convex neural networks}.''}
		% $250 award
		\item NeurIPS Scholar Award
		\cvdate{Oct.\ 2023}
		% $2,000 for travel support
		\item \href{https://sites.google.com/view/duke-engineering-define/home}{DEFINE program attendee}, Duke University
		\cvdate{Oct.\ 2023} \\
		\textit{Selective future faculty workshop emphasizing socially engaged academic leadership.}
		% 27 selectees out of over 80 applicants
		\item \href{https://me.berkeley.edu/me-rising-stars/}{Rising Star in Mechanical Engineering}
		\cvdate{Oct.\ 2023} \\
		\textit{Selected for commitment to building an equitable and diverse scholarly environment through research, teaching, and service.}
		% ~30 awards out of over 100 nominations
		\item Second place method on \href{https://robustbench.github.io/#div_cifar100_Linf_heading}{RobustBench} CIFAR-100 $\ell_\infty$-leaderboard
		\cvdate{May 2023} \\
		\textit{For the paper ``\href{https://bai-yt.github.io/files/publications/AdaptiveSmoothing_PrePrint.pdf}{Improving the accuracy-robustness trade-off of classifiers via adaptive smoothing}.''}
		\item Mechanical Engineering Summer Fellowship, UC Berkeley
		\cvdate{May 2023}
		% $11,000 stipend
		\item \href{https://gsi.berkeley.edu/programs-services/award-programs/ogsi/ogsi-recipients-2022-2023/}{Outstanding Graduate Student Instructor Award}, UC Berkeley
		\cvdate{Mar.\ 2023} \\
		\textit{Schoolwide award for teaching excellence.}
		% At most 10% of graduate student instructors awarded
		\item INFORMS Data Mining Best Student Paper Award runner-up
		\cvdate{Oct.\ 2022} \\
		\textit{For the paper ``\href{https://brendon-anderson.github.io/files/publications/pfrommer2023projected.pdf}{Projected randomized smoothing for certified adversarial robustness}.''}
		\item Graduate Division Block Grant Award, UC Berkeley
		\cvdate{May 2022}
		% $11,000 stipend
		\item John and Janet McMurtry Fellowship, UC Berkeley
		\cvdate{Dec.\ 2020} \\
		\textit{Departmental award for academic excellence, sole recipient.}
		% $22,000 stipend and $20,000 fee payments
		\item Travel Support Award, Conference on Decision and Control
		\cvdate{Dec.\ 2020}
		% $100 for registration payments
		\item Graduate Assembly Professional Development Award, UC Berkeley
		\cvdate{Aug.\ 2020}
		% $200 towards professional development
		\item Graduate Division Block Grant Award, UC Berkeley
		\cvdate{May 2019}
		% $11,000 stipend
		\item \href{https://samueli.ucla.edu/2018-ucla-samueli-commencement-awards/}{Harry M. Showman Prize}, UCLA
		\cvdate{Jun.\ 2018} \\
		\textit{Schoolwide research award, sole undergraduate recipient.}
		% $500 monetary award included
		\item ICINCO Best Student Paper Award shortlisted candidate
		\cvdate{Jun.\ 2018} \\
		\textit{For the paper ``\href{https://arxiv.org/pdf/1806.02488.pdf}{Quantitative assessment of robotic swarm coverage}.''}
		\item Jonathan David Wolfe Memorial Scholarship, UCLA
		\cvdate{Apr.\ 2018} \\
		\textit{Departmental award for academic excellence, one of two recipients.}
		% $1,000 monetary award included
	\end{enumerate}
	
	% publications
	\nocite{*}
	\bibliography{publications}
	
	% invited talks
	\section{\texorpdfstring{Invited Talks \\[\baselineskip] and Poster \\ Presentations}{Invited Talks and Poster Presentations}}
	\hfill\vspace*{-3\baselineskip}
	\begin{enumerate}[label={\arabic*.}]
		\item University of Washington, Seattle, WA \cvdate{Jan.\ 2024}\\
		``Provably robust machine learning through structure-aware computation.'' Department of Applied Mathematics seminar talk.
		\item INFORMS Annual Meeting, Indianapolis, IN \cvdate{Oct.\ 2022}\\
		``Projected randomized smoothing for certified adversarial robustness.'' Research talk.
		\item NorCal Control Workshop, UC Santa Cruz, Santa Cruz, CA \cvdate{June 2022}\\
		``Certified robustness via locally biased randomized smoothing.'' Research poster presentation.
		\item Tsinghua-Berkeley Shenzhen Institute, Berkeley, CA \cvdate{May 2022}\\
		``Robust neural networks.'' Guest lecture for \textit{Optimization Theory and Machine Learning}.
		\item INFORMS Annual Meeting, Anaheim, CA \cvdate{Oct.\ 2021}\\
		``Data-driven certification of neural networks with random inputs.'' Research talk.
		\item Tsinghua-Berkeley Shenzhen Institute, Berkeley, CA \cvdate{May 2021}\\
		``Robust neural networks.'' Guest lecture for \textit{Optimization Theory and Machine Learning}.
		\item University of Michigan, Ann Arbor, MI \cvdate{Apr.\ 2021}\\
		``Robust neural networks.'' Guest lecture for \textit{Advanced Topics in Applied Data Analytics} (IOE 491).
		\item INFORMS Annual Meeting, National Harbor, MD \cvdate{Nov.\ 2020}\\
		``Partition-based convex relaxations for robustness certification of ReLU neural networks.'' Research talk.
		\item Conference on Control Technology and Applications, Montr\'eal \cvdate{Aug.\ 2020}\\
		``Robustness analysis of neural networks.'' Tutorial session.
		\item Institute for Pure and Applied Mathematics, Los Angeles, CA \cvdate{Aug.\ 2017}\\
		``Robotic swarm analysis.'' Research talk.
	\end{enumerate}
	
	% teaching
	\section{Teaching}

	\subsection{Instructor --- Cal Poly}
	\begin{enumerate}[label={\arabic*.}]
		\item \textit{Engineering Dynamics} (ME 212) \cvdate{Fall 2024}
		\item \textit{Introduction to Mechanical Engineering I} (ME 128) \cvdate{Fall 2024}
	\end{enumerate}

	\vspace*{\subsectionskip}

	\subsection{REU Mentor --- UC Berkeley}
	\cvdate{Summer 2023}
	
	\begin{adjustwidth}{\sectionwidth}{}Mentor for \href{https://eecs.berkeley.edu/resources/undergrads/research/superb}{SUPERB Research Experience for Undergraduates (REU)} program, UC Berkeley Electrical Engineering and Computer Sciences (EECS) Department.\end{adjustwidth}

	\subsubsection{Mentee}
	\href{https://www.linkedin.com/in/owen-frausto-39786a217}{Owen Frausto}
	
	\subsubsection{Project}
	``Robust optimal transport over dynamical systems''
	
	\vspace*{\subsectionskip}
	
	\subsection{Graduate Student Instructor --- UC Berkeley}
	\begin{enumerate}[label={\arabic*.}]
		\item \href{https://people.eecs.berkeley.edu/~sojoudi/Course_EE128_SP_2024.html}{\textit{Feedback Control Systems}} (EE C128/ME C134) \cvdate{Spring 2024} \\
		Student ratings: Mean $90.8\%$, Median $100\%$, Standard deviation $20.2\%$.
		\item \href{https://classes.berkeley.edu/content/2023-fall-eleng-227bt-001-lec-001}{\textit{Convex Optimization}} (EE 227BT) \cvdate{Fall 2023} \\
		Student ratings: Mean $97.1\%$, Median $100\%$, Standard deviation $6.1\%$.
		\item \href{https://classes.berkeley.edu/content/2022-fall-eleng-227bt-001-lec-001}{\textit{Convex Optimization}} (EE 227BT) \cvdate{Fall 2022} \\
		\textbf{\href{https://gsi.berkeley.edu/programs-services/award-programs/ogsi/ogsi-recipients-2022-2023/}{Recipient of the Outstanding Graduate Student Instructor Award}}. \\
		Student ratings: Mean $97.3\%$, Median $100\%$, Standard deviation $6.7\%$.
		\item \href{https://lavaei.ieor.berkeley.edu/Course_IEOR160_Fall_2021.html}{\textit{Nonlinear and Discrete Optimization}} (IEOR 160) \cvdate{Fall 2021} \\
		Student ratings: Mean $93.4\%$, Median $100\%$, Standard deviation $9.6\%$.
		\item \href{https://lavaei.ieor.berkeley.edu/Course_IEOR160_Fall_2020.html}{\textit{Nonlinear and Discrete Optimization}} (IEOR 160) \cvdate{Fall 2020} \\
		Student ratings: Mean $90.8\%$, Median $100\%$, Standard deviation $15.2\%$.
	\end{enumerate}
	
	\vspace*{\subsectionskip}

	\subsection{Guest Lecturer --- UC Berkeley}

	\begin{enumerate}[label={\arabic*.}]
		\item \href{https://lavaei.ieor.berkeley.edu/Course_IEOR160_Fall_2022.html}{\textit{Nonlinear and Discrete Optimization}} (IEOR 160) \cvdate{Fall 2022}
		\item \href{https://lavaei.ieor.berkeley.edu/Course_IEOR162_Fall_2022.html}{\textit{Linear Programming and Network Flows}} (IEOR 162) \cvdate{Fall 2022}
		\item \href{https://lavaei.ieor.berkeley.edu/Course_IEOR160_Fall_2021.html}{\textit{Nonlinear and Discrete Optimization}} (IEOR 160) \cvdate{Fall 2021}
	\end{enumerate}

	\vspace*{\subsectionskip}
	
	\subsection{Supplemental Instructor --- Palomar College}	
	\begin{enumerate}[label={\arabic*.}]
		\item \textit{Electromagnetism} (PHYS 231) \cvdate{Spring 2015}
		\item \textit{General Chemistry} (CHEM 115) \cvdate{Fall 2014, Spring 2015}
	\end{enumerate}

	\newpage
	% professional activities
	\section{\texorpdfstring{Professional \\[\baselineskip] Activities}{Professional Activities}}
	\hfill\vspace*{-2\baselineskip}
	\begin{enumerate}[label={\arabic*.}]
		\item Reviewer for International Conference on Learning Representations (ICLR), 2024.
		\item Reviewer for Conference on Neural Information Processing Systems (NeurIPS), 2024
		\item Reviewer for Conference on Decision and Control (CDC), 2024.
		\item Reviewer for International Conference on Machine Learning (ICML) Workshops, 2024.
		\item Reviewer for International Conference on Machine Learning (ICML), 2024.
		\item Reviewer for IEEE Transactions on Automatic Control, 2024.
		% \item NSF grant proposal co-author, 2023.
		\item Reviewer for International Conference on Learning Representations (ICLR), 2023.
		\item Reviewer for IEEE Transactions on Automatic Control, 2023.
		\item Co-organizer of the \href{https://www.ml-verification.com/2023}{$2$nd Workshop on Formal Verification of Machine Learning (WFVML)}, International Conference on Machine Learning (ICML), 2023.
		\item Reviewer for Conference on Neural Information Processing Systems (NeurIPS), 2023.
		\item Reviewer for Conference on Decision and Control (CDC), 2023.
		\item Co-chair of the second morning session, NorCal Control Workshop, 2023.
		\item Reviewer for International Conference on Machine Learning (ICML), 2023.
		\item Reviewer for Learning for Dynamics and Control Conference (L4DC), 2023.
		\item Reviewer for Conference on Neural Information Processing Systems (NeurIPS), 2022.
		\item Reviewer for Conference on Decision and Control (CDC), 2022.
		\item Organizer and co-chair of the session ``Safety and Robustness in Machine Learning,'' INFORMS Annual Meeting, 2022.
		\item Reviewer for IEEE Control Systems Letters, 2022.
		\item Reviewer for IEEE Open Journal of Control Systems, 2022.
		\item Organizer and co-chair of the session ``Robustness of Neural Networks,'' INFORMS Annual Meeting, 2021.
		\item Reviewer for Conference on Decision and Control (CDC), 2021.
		\item Reviewer for IEEE Transactions on Automatic Control, 2021.
		\item Reviewer for Artificial Intelligence and Statistics Conference (AISTATS), 2020.
		\item Reviewer for American Control Conference (ACC), 2020.
		% \item Grant proposal contributor; assisted with writing DARPA funding proposal, 2019.
		\item Chair of the session ``Data Analytics,'' 57th Annual Allerton Conference on Communication, Control, and Computing, 2019.
	\end{enumerate}
	
	% outreach
	\section{Outreach}
	\begin{enumerate}[label={\arabic*.}]
		\item Peer Advisor for the Bay Area Graduate Pathways to STEM (GPS) program, hosted by UC Berkeley Engineering and Stanford Engineering, 2023.
		\item Graduate Student Mentor for incoming students, hosted by UC Berkeley Mechanical Engineering Graduate Student Council, 2023.
		\item Volunteer for \href{https://www.collegeskateboarding.com/}{College Skateboarding Educational Foundation (CSEF)}, 2023. \\
		\textit{Community event organizer to promote scholarships for skateboarders and to foster academia's inclusion of skateboarders from diverse backgrounds.}
		\item Graduate Student Mentor for incoming students, hosted by UC Berkeley Mechanical Engineering Graduate Student Council, 2022.
		\item Graduate Student Mentor for incoming students, hosted by UC Berkeley Mechanical Engineering Graduate Student Council, 2021.
		\item Peer Advisor for the Bay Area Graduate Pathways to STEM (GPS) program, hosted by UC Berkeley Engineering and Stanford Engineering, 2020.
	\end{enumerate}
	
	% relevant coursework
	\begin{coursework}
		\section{\texorpdfstring{Relevant \\[\baselineskip] Coursework}{Relevant Coursework}}
		\hfill\vspace*{-2\baselineskip}
		
		\subsection{Optimization}
		\begin{enumerate}[label={\arabic*.}]
			\item \textit{Nonlinear Programming}, Professor Javad Lavaei
			\item \textit{Convex Optimization}, Professors Somayeh Sojoudi and Laurent El Ghaoui
			\item \textit{Optimization Models}, Professors Laurent El Ghaoui and Alex Bayen
		\end{enumerate}
		
		\vspace*{\subsectionskip}
		
		\subsection{Machine Learning}
		\begin{enumerate}[label=\arabic*.]
			\item \textit{Statistical Learning Theory} (audit), Professors Ben Recht and Moritz Hardt
			\item \textit{Learning and Optimization}, Professor Anil Aswani
			\item \textit{Deep Learning} (online), Professor Andrew Ng
			\item \textit{Machine Learning} (online), Professor Andrew Ng
		\end{enumerate}
		
		\vspace*{\subsectionskip}
		
		\subsection{Dynamical Systems and Control Theory}
		\begin{enumerate}[label=\arabic*.]
			\item \textit{Nonlinear Systems: Analysis, Stability, and Control}, Professor Claire Tomlin
			\item \textit{Advanced Control Theory II} (LQ control, stochastic estimation and control, tracking and adaptive control), Professor Masayoshi Tomizuka
			\item \textit{Advanced Control Theory I} (linear systems, Lyapunov stability, state observer feedback, LQR), Professor Roberto Horowitz
			\item \textit{Linear Dynamical Systems}, Professor Robert M'Closkey
			\item \textit{Digital Control}, Professor Tsu-Chin Tsao
		\end{enumerate}
		
		\vspace*{\subsectionskip}
		
		\subsection{Mathematics}
		\begin{enumerate}[label=\arabic*.]
			\item \textit{Groups, Rings, and Fields}, Professor Richard Borcherds
			\item \textit{Diffierentiable Manifolds}, Professor Richard Bamler
			\item \textit{Topology and Analysis II} (functional analysis), Professor Michael Christ
			\item \textit{Topology and Analysis I} (measure theory), Professor Alan Hammond
			\item \textit{Engineering Mathematics} (single course: linear algebra, optimization, and probability), Professors Andrew Packard, Somayeh Sojoudi, and Kameshwar Poolla
			\item \textit{Analysis} (\textit{Real}; \textit{Complex}; \textit{Numerical})
			\item \textit{Differential Equations} (\textit{Ordinary}; \textit{Partial})
		\end{enumerate}
		
		\vspace*{\subsectionskip}

		\subsection{Statistics}
		\begin{enumerate}[label=\arabic*.]
			\item \textit{Theoretical Statistics II} (high-dimensional), Professor Yan Shuo Tan
			\item \textit{Theoretical Statistics I} (classical), Professor Will Fithian
		\end{enumerate}

		\vspace*{\subsectionskip}

		\subsection{Game Theory}
		\begin{enumerate}[label=\arabic*.]
			\item \textit{Population Games}, Professor Murat Arcak
		\end{enumerate}
	\end{coursework}

	% references
	\begin{references}
	\section{References}

	\subsection{Somayeh Sojoudi}
	\cvdates{}{}

	\begin{adjustwidth}{\sectionwidth}{}
	Associate Professor

	Electrical Engineering and Computer Sciences

	University of California, Berkeley
	
	Email: \href{mailto:sojoudi@berkeley.edu}{\texttt{sojoudi@berkeley.edu}}

	Website: \url{https://people.eecs.berkeley.edu/~sojoudi/}
	\end{adjustwidth}

	\vspace*{\subsectionskip}

	\subsection{Javad Lavaei}
	\cvdates{}{}

	\begin{adjustwidth}{\sectionwidth}{}
	Associate Professor

	Industrial Engineering and Operations Research

	University of California, Berkeley

	Email: \href{mailto:lavaei@berkeley.edu}{\texttt{lavaei@berkeley.edu}}

	Website: \url{https://lavaei.ieor.berkeley.edu/}
	\end{adjustwidth}
	
	\vspace*{\subsectionskip}

	\subsection{Murat Arcak}
	\cvdates{}{}

	\begin{adjustwidth}{\sectionwidth}{}
	Professor

	Electrical Engineering and Computer Sciences

	University of California, Berkeley

	Email: \href{mailto:arcak@berkeley.edu}{\texttt{arcak@berkeley.edu}}

	Website: \url{https://people.eecs.berkeley.edu/~arcak/}
	\end{adjustwidth}

	\vspace*{\subsectionskip}

	\subsection{Matthew Powell-Palm}
	\cvdates{}{}

	\begin{adjustwidth}{\sectionwidth}{}
	Assistant Professor

	Mechanical Engineering

	Texas A\&M University

	Email: \href{mailto:powellpalm@tamu.edu}{\texttt{powellpalm@tamu.edu}}

	Website: \url{https://publicthermo.com/}
	\end{adjustwidth}
	\end{references}
	
\end{document}
